---
title: "Penguin Flipper Length and Body Mass in R"
author: "Fang Fang"
date: 2026-09-26
---

Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/),
Palmer Station Antarctica LTER.
Horst AM, Hill AP, Gorman KB (2020). palmerpenguins: Palmer Archipelago (Antarctica) penguin data. R package version 0.1.0. https://allisonhorst.github.io/palmerpenguins/. doi:10.5281/zenodo.3960218.

In this post, I will compare penguins flipper length and body mass using the Palmer Penguins dataset.

```{r}
#| message: false
#| warning: false

library(palmerpenguins)
library(tidyr)
library(dplyr)
penguins <- palmerpenguins::penguins
head(penguins)
```

Before proceeding the analysis, I clean the data first by removing na values in flipper length and body mass. 
For convenience, I also only keep the columns I want to study with.

```{r}
penguins_data <- penguins |>
    select(species,flipper_length_mm,body_mass_g) |>
    drop_na()
```

Next, I calculate the average flipper length and body mass for each species.

```{r}
penguins_data |>
    group_by(species) |>
    summarise(mean_flipper_length_mm = mean(flipper_length_mm),
        mean_body_mass_g = mean(body_mass_g))
```

To study the relation between Flipper Length and Body Mass, I calculate the correlation.

```{r}
cor(penguins_data$flipper_length_mm, penguins_data$body_mass_g)
```

After that, I plot Flipper Length and Body Mass into graph

```{r}
#| label: fig-penguins-flipper-mass
#| fig-cap: "Flipper length and body mass of Palmer penguins."

plot(penguins_data$flipper_length_mm,
    penguins_data$body_mass_g,
    xlab = "Flipper length (mm)",
    ylab = "Body mass (g)")
```

This plot shows a positive, approximately linear relation between Flipper length and body mass. That is also intuitive, penguins with longer flippers tend to be heavier.